---
title: "Development notes"
author: "Sara"
date: "`r format(Sys.Date(), '%d %b %Y')`"
format: 
  html:
    self-contained: true
---

# Technical stuff

- where should I run the data loading?
- where can I load the data so that it is also accessible to the ui? (needed for sensible input choices)
- how can/should I test the module?
- how can I add an about page? from html? from Rmarkdown? from Markdown?

# UI considerations

- make the module in a kind of card?
- general layout? add text/about/possibly another plot
- the map legend is tiny
- not sure about the table [widths](https://glin.github.io/reactable/articles/examples.html#column-resizing), column names, their alignment etc.
- general low-key effort to improve the table?
- what kind of input? drop down, radio button, ...
- mobile? 


# Content considerations

## Locations

it would be nice to add the locations from where the emergency services start?
see [ambulances](https://www.stadt-zuerich.ch/pd/de/index/schutz_u_rettung_zuerich/sanitaet/so_arbeiten_wir/rettungsdienstwachen.html) and [fire services](https://www.stadt-zuerich.ch/pd/de/index/schutz_u_rettung_zuerich/feuerwehr/wir_ueber_uns/einsatzgebiet.html)
would have to manually parse/add those 6 addresses to a small dataset
some of the bases are outside the city itself... never mind.

## Lake

Better to take out the lake in the map?

# Concrete todos

- [x] write ReadMe
- [x] load data in better place - probably not ideal but seems to work
- [x] make year selector choices dependent on data - probably not ideal but seems to work
- [x] correct sorting of 'stadtkreise' - needs a javascript function!!
- [x] make language consistently English
- [x] adjust colors of map and bars
- [x] make a navbar page with ambulance, fire services
- [x] add tabPanel with About Page
- [ ] improve header alignment - needs help; most promising [post](https://groups.google.com/g/shiny-discuss/c/DVF2YQeYfiE) - but from 2015 and nothing changed...
- [ ] make map interactive, see [plotly documentation](https://plotly.com/r/choropleth-maps/) - does not work with quantiles??
- [ ] add locations of ambulance/fire service bases to the map- lower priority
- [ ] deploy (automatically) to shinyapps.io
- [ ] update readme
- [ ] make the repo public
- write tests
  - [ ] for data reading - make sure I have the columns in the data that I need in the plot and table
  - [ ] for plotting - okish
  - [ ] for the module - okish
- emergency calls - low priority
  - [ ] play around with the date and come up with a good plot
  - [ ] make a new module for this (is it interactive?)
  - [ ] decide on and adjust overall UI
  
## finding all dependencies
apparently I need the markdown package to include markdown (about page). this could not be automatically detected with `attachment::att_amend_desc()`, so I ran

```{r eval=FALSE}
usethis::use_package( "markdown" ) # To call each time you need a new package
usethis::use_pipe()
```

The pipe was also an issue. What is the correct way of dealing with dependencies?
  
## filtering

using a named vector as the 'stadtkreis' column does not work, reactable does not show the label, it still shows the value
```{r eval=FALSE}
stadtkreise_num <- as.numeric(stringr::str_extract(ambulance$stadtkreis, "[:digit:]+"))
names(stadtkreise_num) <- ambulance$stadtkreis
ambulance$stadtkreis <- stadtkreise_num
put_data_in_table(ambulance, 2020)
# filtering won't work
```

using factors probably won't work either as [this issue](https://github.com/glin/reactable/issues/202) is still open

the [examples](https://glin.github.io/reactable/articles/custom-filtering.html#regular-expression-pattern-filtering) say I can add a custom filtering function but it needs to be in javascript...--> ask course instructors

works with separate function, similar to the bar chart one

# known issues

- data loading function is called directly where it is defined in the utils. pro: this makes the data available to the ui and the server and means this is run before the app is started. con: does not feel like a clean way of doing things?
