---
title: "Development notes"
author: "Sara"
date: "`r format(Sys.Date(), '%d %b %Y')`"
format: 
  html:
    self-contained: true
---

# Technical stuff

- where should I run the data loading? --> asked question on stackoverflow
- shiny module does not work with bind cache if I have several instances? --> asked question on stackoverflow

# Content considerations

## Lake

Better to take out the lake in the map? postponed.

## Header alignment

only seems aligned if the text is within a module. Currently (slightly hacky) it is hardcoded within the module. I could also have an extra module just for the title.
same problem without an answer from 7y ago [post](https://groups.google.com/g/shiny-discuss/c/DVF2YQeYfiE)

things that do not lead to the same alignment:

- `p` or `fluidRow` within the app's main ui
- `header = column(12, "Response times of the emergency services in the city of Zurich.")`  within the navbar page of the app's main ui; it is better/more to the right, but still not aligned with the content of the module

# Concrete todos

- [x] write ReadMe
- [x] load data in better place - probably not ideal but seems to work
- [x] make year selector choices dependent on data - probably not ideal but seems to work
- [x] correct sorting of 'stadtkreise' - needs a javascript function!!
- [x] make language consistently English
- [x] adjust colors of map and bars
- [x] make a navbar page with ambulance, fire services
- [x] add tabPanel with About Page
- [x] try horizontal radio buttons
- [x] make map interactive
- [x] deploy (automatically) to shinyapps.io
- [x] update readme
- [x] make the repo public
- [x] try without exporting the pipe - works too. next time use `export = FALSE`
- [x] try with caching of plots
- [x] add hint to user that something is being plotted - could use shinycssloader, but it is kind of overkill

## finding all dependencies
apparently I need the markdown package to include markdown (about page). this could not be automatically detected with `attachment::att_amend_desc()`, so I ran

```{r eval=FALSE}
usethis::use_package( "markdown" ) # To call each time you need a new package
usethis::use_pipe()
```

The pipe was also an issue...
  
## filtering

using a named vector as the 'stadtkreis' column does not work, reactable does not show the label, it still shows the value
```{r eval=FALSE}
stadtkreise_num <- as.numeric(stringr::str_extract(ambulance$stadtkreis, "[:digit:]+"))
names(stadtkreise_num) <- ambulance$stadtkreis
ambulance$stadtkreis <- stadtkreise_num
put_data_in_table(ambulance, 2020)
# filtering won't work
```

using factors probably won't work either as [this issue](https://github.com/glin/reactable/issues/202) is still open

the [examples](https://glin.github.io/reactable/articles/custom-filtering.html#regular-expression-pattern-filtering) say I can add a custom filtering function but it needs to be in javascript...--> ask course instructors

works with separate function, similar to the bar chart one

# known issues

- data loading function is called directly where it is defined in the utils. pro: this makes the data available to the ui and the server and means this is run before the app is started. con: does not feel like a clean way of doing things?
